The imprint of global magma oceans on exoplanet demographics

### 2023-01-14 src/tex/ms.tex
let python write variables to LaTeX
add figure with different PLATO surveys
Figure is going to need some further polishing.

\begin{figure}[ht!]
%    \script{figurescript.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/corner.pdf}
        \caption{
            Retrieved posterior distribution of key parameters in the optimistic scenario. The density maps in each panel show relationships between and marginalized distributions of the model parameters as they could be retrieved with a high-precision transit survey and a sample of \Nplanets\ planets. True values of the parameters for the injected effect are shown in orange. The threshold instellation can be well constrained; the predominant water fraction and the fraction of planets with runaway greenhouse climates are degenerate.
        }
        \label{fig:cornerplot}
    \end{centering}
\end{figure}
With such a strong signal, we can attempt an inference of the parameters defining the injected effect.
Figure~\ref{fig:cornerplot} shows the posterior distributions of $S_\mathrm{thresh}$, $x_{H_2O}$, and $f_\mathrm{rgh}$ as determined by the nested sampler.
The threshold instellation can be accurately constrained, $S_\mathrm{thresh}$ = \retrSthresh.
Both a higher water mass fraction and a higher fraction of planets in a runaway greenhouse state lead to larger average radii, thus these parameters are strongly correlated and cannot be well constrained without independent measurements.

@@

>>>>

\begin{figure}[ht!]
%    \script{figurescript.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/corner.pdf}
        \caption{
            Retrieved posterior distribution of key parameters in the optimistic scenario. The density maps in each panel show relationships between and marginalized distributions of the model parameters as they could be retrieved with a high-precision transit survey and a sample of \Nplanets\ planets. True values of the parameters for the injected effect are shown in orange. The threshold instellation can be well constrained; the predominant water fraction and the fraction of planets with runaway greenhouse climates are degenerate.
        }
        \label{fig:cornerplot}
    \end{centering}
\end{figure}
With such a strong signal, we can attempt an inference of the parameters defining the injected effect.
Figure~\ref{fig:cornerplot} shows the posterior distributions of $S_\mathrm{thresh}$, $x_{H_2O}$, and $f_\mathrm{rgh}$ as determined by the nested sampler.
The threshold instellation can be accurately constrained, $S_\mathrm{thresh} = \var{retrSthresh}$.
Both a higher water mass fraction and a higher fraction of planets in a runaway greenhouse state lead to larger average radii, thus these parameters are strongly correlated and cannot be well constrained without independent measurements.

@@

    \begin{figure}[ht!]
%    \script{figurescript.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/plato_fgrid.pdf}
            \caption{
            Expected evidences as a function of the fraction of planets harboring runaway greenhouse climates for different versions of the \plato\ survey.
            $\Delta \ln Z > 3$ (gray horizontal line) is considered sufficient evidence to reject the null hypothesis.
            For a large planet yield of $N = \var{Nplato}$, even small planet fractions $\gtrsim \var{platoMinfrgh}$ allow a detection.
                A much smaller sample of 100 planets is sufficient if their masses are constrained to within \SI{10}{\percent} (dashed green line).
                Without such follow-up measurements, sufficient diagnostic power can only be achieved with this sample if $f_\mathrm{rgh} \gtrsim \var{platoMinfrghHundred}$.
               Even smaller samples are unlikely to yield a significant detection.
            }
            \label{fig:plato_fgrid}
        \end{centering}
    \end{figure}

For a volume-limited sample of \var{Nplato} planets, considering all host star spectral types, we find that \plato\ is able to obtain a significant detection if the fraction of runaway greenhouse planets is larger than $\sim \var{platoMinfrgh}$ (see Fig.~\ref{fig:plato_fgrid}).
The minimum needed fraction rises to \var{platoMinfrghHundred} for $N = 100$.
For much smaller samples, even an optimistically strong signal can no longer be detected.
